ICBEdataset figure Metro Maps

### 2022-03-22 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
tree fix

#Lit review
#child=c('ICBEdataset_paper_litreviewtable.Rmd')
flextable::set_flextable_defaults(fonts_ignore=TRUE)
library(flextable)
library(ftExtra)
litreview_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/litreview_ft.Rds'))

@@

litreview_ft %>%
  flextable::set_caption(caption = "Prior Beliefs, State of the Art, and Existing Data") %>%
  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
  flextable_to_rmd()
```

>>>>

#Lit review
#child=c('ICBEdataset_paper_litreviewtable.Rmd')
library(flextable)
library(ftExtra)
flextable::set_flextable_defaults(fonts_ignore=TRUE)
litreview_ft  <- readRDS(file=paste0(here::here(), '/replication_paper/tables/litreview_ft.Rds'))

@@

litreview_ft %>%
  flextable::set_caption(caption = "Prior Beliefs, State of the Art, and Existing Data") %>%
  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
  flextable::flextable_to_rmd()
```

### 2022-03-22 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
tree fix

  dyadic_mid_clean_dyad <- 
    bind_rows(
      incident_mid_clean_subset %>% 
        mutate(label=
                 paste0( act_1_label %>% replace_na(''),", ", revtype1_2_label %>% replace_na('') ,", ", fatality_1_label %>% replace_na('')) %>% trimws() %>%
                 str_replace_all("None|Not applicable","") %>% trimws() %>% str_replace("^,|,$|","") %>% trimws()
               ) %>%
        dplyr::select(stday, stmon, styear, endday, start,   end, start, actor_1=actor_1,actor_2=actor_2, leaf=label) 
  ) %>%
    mutate(sent= start %>% rank() %>% round())

>>>>

  dyadic_mid_clean_dyad <- 
    bind_rows(
      incident_mid_clean_subset %>% 
        mutate(label=
                 paste0( act_1_label %>% tidyr::replace_na(''),", ", revtype1_2_label %>% tidyr::replace_na('') ,", ", fatality_1_label %>% tidyr::replace_na('')) %>% trimws() %>%
                 str_replace_all("None|Not applicable","") %>% trimws() %>% str_replace("^,|,$|","") %>% trimws()
               ) %>%
        dplyr::select(stday, stmon, styear, endday, start,   end, start, actor_1=actor_1,actor_2=actor_2, leaf=label) 
  ) %>%
    mutate(sent= start %>% rank() %>% round())
